THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-20 DishReflectometry/Paper1_v3.tex
Tweaks to intro and S1

    \newcommand{\vdag}{(v)^\dagger}
    \newcommand{\volt}{{v}}
    \newcommand{\vis}{{V}}
    \newcommand{\sky}{{\rm sky}}
    \newcommand{\bmvolt}{{a}}
    \newcommand{\beam}{{A}}
    \newcommand{\thhat}{{\hat\theta}}
    \newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
    \newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
    \newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
    %\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

    \indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array
    consisting of 568 14-m dishes in South Africa which will measure the 21~cm
    power spectrum between 100 to 200~MHz.
    In this paper, we investigate the performance of an individual HERA element and
    the resulting manifestation of the instrument response to the delay spectrum.
    Reflectometry measurements  are carried out across a wide bandwidth on a
    prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
    results are interpreted in light of the delay spectrum technique of power
    spectrum estimation and inverse covariance weighting method of foreground
    suppression. Section 2 briefly describes the delay spectrum for the ideal and
    non-ideal performance of a two element interferometer. Section 3 describes the
    reflectometry measurements and establishes the connection between visibility
    measurements and reflectometry. Reflectometry results are described in section
    5. Section 6 evaluates the performance of the HERA element for detection of the
    21~cm power spectrum.

    This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}. We compare 
    reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}. 
    \begin{figure*}
    \centering
    \includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
    \caption{HERA dish feed at the Green Bank NRAO site.}
    \label{fig:heradish}
    \end{figure*}

    \section{\textbf{Visibility measurements by a two element interferometer and the delay spectrum}}
    Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,

    \begin{equation}
    \volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
    \end{equation}
    \begin{equation}
    \volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
    \end{equation}
    Hence, the time averaged visibility measured by the interferometer may be written as, 
    \begin{equation}
    \vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
    \label{eq1}
    \end{equation}

    We define the antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$. Hence, 
    \begin{equation}
    \vis(\vec b,\nu) = \int \beam(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
    	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
     	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
    	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
    	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
    \label{eq2}
    \end{equation}

    %i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
    In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
    resulting in the delay spectrum:
    \begin{eqnarray}
    \tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
    \label{eq3}
    \end{eqnarray}
    % XXX rethink how to express this equation (not correct about integrated over all sky)
    % XXX define tau_g
    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
    The redshifted 21 cm spatial power spectrum is defined as
    \begin{equation}
      P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
    \label{eq4}
    \end{equation}
    where
    \begin{equation}
      k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
      k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
     \label{eq5}
    \end{equation}
    The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
    $f_{21}$:rest frame frequency of the 21~cm radiation.\\
    $f$: observation frequency.\\
    $z$: cosmological redshift corresponding to the frequency of observation.\\
     $\Delta B$: bandwidth centered at the observation frequency.\\
     $k_\textrm{B}$: Boltzmann constant.\\
     $D\equiv D(z)$ comoving distance along the line of sight\\
     $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
    $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
    \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

>>>>

    \newcommand{\vdag}{(v)^\dagger}
    \newcommand{\volt}{{v}}
    \newcommand{\vis}{{V}}
    \newcommand{\sky}{{\rm sky}}
    \newcommand{\bmvolt}{{a}}
    \newcommand{\beam}{{A}}
    \newcommand{\thhat}{{\hat\theta}}
    %\newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
    %\newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
    \newcommand{\fngexp}{{e^{2\pi i\nu\vec{b}\cdot\thhat/c}}}
    \newcommand{\ifngexp}{{e^{-2\pi i\nu\vec{b}\cdot\thhat/c}}}
    \newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
    %\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

    \begin{figure*}
    \centering
    \includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
    \caption{HERA dish feed at the Green Bank NRAO site.}
    \label{fig:heradish}
    \end{figure*}

    In this paper, we use reflectometry measurements to
    investigate the delay-domain performance of 
    the 14-m parabolic dish elements (Figure \ref{fig:heradish}) that are proposed to be used in HERA, operating 
    from 100 to 200~MHz.
    %Reflectometry measurements are carried out across a wide bandwidth on a
    %prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
    %results are interpreted in light of the delay spectrum technique of power
    %spectrum estimation and inverse covariance weighting method of foreground
    %suppression. 
    This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}. We compare 
    reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}. 
    In this paper, Section 2 briefly describes the delay spectrum for the ideal and
    non-ideal performance of a two element interferometer. Section 3 describes the
    reflectometry measurements and establishes the connection between visibility
    measurements and reflectometry. Reflectometry results are described in Section
    5. Section 6 evaluates the performance of the HERA element for detection of the
    21~cm power spectrum.

    \section{\textbf{Visibility measurements by a two element interferometer in the delay domain}}

    Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,

    \begin{equation}
    \volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)~\volt_\sky(\thhat,\nu)\nonumber\\
    \end{equation}
    \begin{equation}
    \volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)~\volt_\sky(\thhat,\nu)~\fngexp\nonumber\\
    \end{equation}
    Hence, the time averaged visibility measured by the interferometer may be written as, 
    \begin{equation}
    \vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)~  \volt_{2}^{*} (\thhat, \nu)~ \ifngexp d\Omega 
    \label{eq1}
    \end{equation}

    We define the antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)~\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)~\volt_\sky^{*}(\thhat,\nu)$. Hence, 
    \begin{equation}
    \vis(\vec b,\nu) = \int \beam(\thhat, \nu)~ I_\sky(\thhat,\nu)~ \ifngexp d\Omega
    	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
     	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
    	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
    	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
    \label{eq2}
    \end{equation}

    %i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
    In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
    resulting in the delay spectrum:
    \begin{eqnarray}
    \tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
    \label{eq3}
    \end{eqnarray}
    % XXX rethink how to express this equation (not correct about integrated over all sky)
    % XXX define tau_g
    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
    It was then shown that the this delay-transformed visibility related to the power spectrum of redshifted
    21 cm emission as
    \begin{equation}
      P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
    \label{eq4}
    \end{equation}
    where
    \begin{equation}
      k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
      k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
     \label{eq5}
    \end{equation}
    The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
    $f_{21}$:rest frame frequency of the 21~cm radiation.\\
    $f$: observation frequency.\\
    $z$: cosmological redshift corresponding to the frequency of observation.\\
     $\Delta B$: bandwidth centered at the observation frequency.\\
     $k_\textrm{B}$: Boltzmann constant.\\
     $D\equiv D(z)$ comoving distance along the line of sight\\
     $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
    $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
    \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
